Empirical Evaluation of eval in R

### 2020-08-14 inst/analysis/analysis_stable.Rmd
Update notebook header and organize package imports

---
title: "analysis_stable"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
date: "`r substr(Sys.time(), 1, 10)`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "center",
  fig.retina = 2,
  fig.width = 10,
  cache.lazy = FALSE
  )

library(tidyverse)
library(stringr)
library(viridis)
library(vctrs)

library(DT)

library(fst)

library(bench)

@@

All insights about eval calls are to put here, after the computations are stabilized (so use another notebook to explore).

# Setup

```{r eval_calls_file}
# All CRAN
#eval_calls_file <- "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"

# Subset (500 packages)
eval_calls_file <- "/var/lib/R/project-evalR/run/package-evals-traced-corpus.1/calls.fst"
```

```{r load_file}
eval_calls <- read_fst(eval_calls_file)
eval_calls <- as_tibble(eval_calls) 
```

```{r resolve_types}
eval_calls <- eval_calls %>% resolve_sexp_name(expr_expression_type) %>% 
                             resolve_sexp_name(expr_resolved_type) %>%
                             resolve_sexp_name(enclos_type) %>%
                             resolve_sexp_name(envir_type)
```

# Description of the columns

```{r, echo = FALSE}
c_names <- names(eval_calls)
column_names <- setNames(data.frame(matrix(ncol = length(c_names), nrow = 0)), c_names)

@@

```

```{r, echo = FALSE}
column_names %>% knitr::kable()

```

# Usage metrics

## Number of `eval`

>>>>

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center",
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE)

library(tidyverse)
library(stringr)
library(viridis)
library(vctrs)
library(DT)
library(fst)

@@

# Data

```{r load-data, echo=FALSE}
eval_calls <-
    read_fst(params$data_filepath) %>%
    as_tibble() %>%
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)

c_names <- names(eval_calls)
column_names <- setNames(data.frame(matrix(ncol = length(c_names), nrow = 0)), c_names)

@@

column_names %>% knitr::kable()
```

# Research Questions

## RQ1: How many evals are there?
